% Derived from cv/cv-full.tex
% Target: 1 page
% Audience: general short CV with brand consistency to the master template
\documentclass[margin,line,pifont,palatino,courier]{res}
% Source: https://www.math.nyu.edu/student_resources/misc.php
\usepackage{pifont}
\usepackage[latin1] {inputenc}
\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{xspace}
\usepackage{tabularx}
\usepackage{booktabs}

\usepackage{fontawesome5}
\usepackage[dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\definecolor{uscred}{rgb}{0.597, 0.105, 0.117}
\definecolor{cmublue}{rgb}{0.093, 0.171, 0.3}
\newcommand{\equalcontrib}{\textsuperscript{$\dagger$}}
\newcommand{\corrauthor}{\textsuperscript{$\spadesuit$}}

\hypersetup{
    colorlinks,
    linkcolor={cmublue},
    citecolor={cmublue},
    urlcolor={cmublue}
}

\usepackage[most]{tcolorbox}

\newtcbox{\mybox}[1][red]{on line,
    colback=#1, colframe=#1, boxsep=0pt, boxrule=0pt, size=small, arc=0.3mm}

\topmargin -.15in
\oddsidemargin -.25in
\evensidemargin -.25in
\textwidth=6.0in
\textheight=9.35in
\usepackage{fancyhdr}
\usepackage{lastpage}
\rightmargin=0.22in

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\lfoot{{\footnotesize Yue Zhao - CV}}
\rfoot{{\footnotesize Last updated: \today. Page \thepage\ of \pageref{LastPage}}}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{{\huge Yue Zhao}\vspace*{.05in}}

\begin{resume}

\section{\sc Contact Information}
\href{mailto:yue.z@usc.edu}{\faEnvelope[regular]~\texttt{yue.z@usc.edu}}  \hfill 213-821-2369
\\
\href{https://github.com/yzhao062}
{\faGithub~\texttt{github.com/yzhao062}}
\hfill CS Department, GCS Hall\\
\href{https://www.linkedin.com/in/yzhao062/}{\faLinkedinIn ~\texttt{linkedin.com/in/yzhao062}}  \hfill Los Angeles, CA \\
\href{https://viterbi-web.usc.edu/~yzhao010/}{\faHome~\url{https://viterbi-web.usc.edu/~yzhao010/}}  \hfill United States, 90089 \\
\href{https://scholar.google.com/citations?user=zoGDYsoAAAAJ}{\faGoogle~\texttt{Google Scholar}}
\hfill University of Southern California\\
{\color{uscred}\faStar~22{,}000+ GitHub Stars \hfill
\href{https://gitstar-ranking.com/yzhao062}{Top $\sim$700 Worldwide}}
\vspace{-0.1in}

\section{\sc Research Summary}
I build the methods, benchmarks, and open-source tools for \textbf{AI auditing}---making
AI systems inspectable, safe, and accountable. This spans how to inspect and evaluate
AI systems (auditing and assurance), what failure modes to audit for (safety and security),
and where accountability is not optional (science and society).
\vspace{-0.12in}

\section{\sc Full-time Professional Experience}
\textbf{University of Southern California} \\
\textit{Thomas Lord Department of Computer Science} \\
Assistant Professor (Tenure-Track) \hfill Aug. 2023 - Present
\begin{list2}
\item Founded the FORTIS Lab and lead research on AI auditing, agent safety, and deployment assurance; affiliated with the USC Machine Learning Center.
\end{list2}
\vspace{-0.08in}

\textbf{PwC Canada} \\
\textit{Consulting \& Deals} \\
Senior Consultant (Data Scientist), Consultant, Research Associate (Intern) \hfill May 2016 - Jun. 2019
\vspace{-0.08in}

\section{\sc Education}
\textbf{Carnegie Mellon University} \hfill Pittsburgh, PA \\
\textit{Ph.D. in Information Systems and Management} \hfill Sep. 2019 - May. 2023

\textbf{University of Toronto} \hfill Toronto, ON\\
\textit{Master of Science in Computer Science} \hfill Sep. 2015 - Dec. 2016

\textbf{University of Cincinnati} \hfill Cincinnati, OH\\
\textit{Bachelor of Science in Computer Engineering} \hfill Sep. 2010 - May. 2015 \\
\textbf{Minor}: \textit{Computer Science} and \textit{Mathematics}
%\vspace{-0.08in}

\section{\sc Selected Systems and Publications}
{\small
\begin{tabular}{@{}p{0.47\textwidth}p{0.47\textwidth}}
\textbf{Open-Source Systems} & \textbf{Selected Publications (104 total)} \\
\begin{minipage}[t]{0.47\textwidth}
\begin{itemize}[leftmargin=*,itemsep=0.08em,topsep=0.08em]
\item \textbf{\href{https://github.com/yzhao062/pyod}{PyOD}} (\textcolor{uscred}{9.8K stars, 39M+ downloads}) Outlier and anomaly detection library.
\item \textbf{\href{https://github.com/Minqi824/ADBench}{ADBench}} (\textcolor{uscred}{1K stars}) Large-scale anomaly detection benchmark.
\item \textbf{\href{https://github.com/yzhao062/anomaly-detection-resources}{Anomaly-Detection-Resources}} (\textcolor{uscred}{9.2K stars}) Curated resource hub for anomaly detection.
\item \textbf{\href{https://github.com/HowieHwong/TrustLLM}{TrustLLM}} (\textcolor{uscred}{620 stars}) Benchmark and toolkit for LLM trustworthiness.
\item \textbf{\href{https://github.com/HeadyZhang/agent-audit}{agent-audit}} (\textcolor{uscred}{146 stars}) Toolkit for auditing AI agent code.
\item \textbf{\href{https://github.com/Justin0504/Aegis}{Aegis}} (\textcolor{uscred}{341 stars}) Runtime firewall and compliance platform for AI agents.
\item \textbf{\href{https://github.com/USC-FORTIS/AD-AGENT}{AD-AGENT}} (\textcolor{uscred}{97 stars}) Multi-agent platform for end-to-end anomaly detection.
\end{itemize}
\end{minipage}
&
\begin{minipage}[t]{0.47\textwidth}
\begin{itemize}[leftmargin=*,itemsep=0.08em,topsep=0.08em]
\item \textit{Defenses Against Prompt Attacks}. \textbf{ACL}, 2026.
\item \textit{Doxing via the Lens}. \textbf{ICLR}, 2026.
\item \textit{Charts Are Not Images}. \textbf{ICLR}, 2026.
%\item \textit{TrustGen}. \textbf{ICLR}, 2026.
\item \textit{Mitigating Hallucinations via Causal Reasoning}. \textbf{AAAI}, 2026.
\item \textit{DPU: Multimodal OOD Detection}. \textbf{CVPR} \faAward~Highlight, 2025.
\item \textit{DyFlow: Agentic Reasoning}. \textbf{NeurIPS}, 2025.
\item \textit{MetaOOD}. \textbf{ICLR}, 2025.
\item \textit{MultiOOD}. \textbf{NeurIPS} \faAward~Spotlight, 2024.
\item \textit{TrustLLM}. \textbf{ICML}, 2024.
%\item \textit{Diffusion Models: A Comprehensive Survey}. \textbf{ACM CSUR}, 2023.
\item \textit{ADBench}. \textbf{NeurIPS}, 2022.
\item \textit{PyOD}. \textbf{JMLR}, 2019.
\end{itemize}
\end{minipage}
\end{tabular}
}
%\vspace{-0.08in}

\section{\textcolor{uscred}{\faAward} \sc Awards, Grants, and Funding}
%\vspace{-0.2in}
{\small
\begin{tabularx}{\textwidth}{@{}Xr@{}}
\href{https://www.nvidia.com/en-us/industries/higher-education-research/academic-grant-program/}{NVIDIA Academic Grant Program}; \href{https://www.amazon.science/research-awards}{Amazon Research Awards} (AI for InfoSec) & 2026 \\
Best Short Paper @ ACM SIGSPATIAL; Second Prize CCC @ IEEE ICDM BlueSky & 2025 \\
\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2449280}{NSF POSE Phase I} & 2025 \\
\href{https://www.amazon.science/research-awards/recipients/yue-zhao}{Amazon Research Awards} (Graph AD); \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2428039}{NSF ATD}; \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2346158}{NSF POSE Phase II} & 2024 \\
\href{https://viterbischool.usc.edu/news/2024/04/usc-and-capital-one-establish-new-center-for-responsible-ai-in-finance/}{Capital One Research Award}; \href{https://cloud.google.com/edu/researchers/innovators}{Google Cloud Research Innovators}; \href{https://aaai.org/aaai-conference/aaai-24-new-faculty-highlights/}{AAAI New Faculty Highlights} & 2024 \\
\end{tabularx}
}

\end{resume}
\end{document}
